Commutative Character Sheaves, with an application to generic types for supercuspidal representations

### 2015-09-06 followup.tex
Commit after conversation with David

\begin{proposition}
Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then $G$ is commutative. 
\end{proposition}

@@

\begin{proof}
By construction, $c : G \times G \to G$ is schematically dense (dominant morphism) for $j : G\der \hookrightarrow G$. 
Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_{G\der})
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}.
\end{align*}
Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$. It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
\end{proof}

@@

[I don't have a proof of this yet.]

\[
\begin{tikzcd}
\CCS(G\der \times G)
& \arrow{l}[shift left,swap]{n^*}
  \arrow{l}[shift right]{p^*}
\CCS(G) 
&&\arrow{ll}[swap]{f^*} 
\CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\
& & \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
\end{tikzcd}
\]

>>>>

\begin{proposition}
Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then it is commutative. 
\end{proposition}

@@

\begin{proof}
By construction, $c : G \times G \to G\der$ is dominant. 
Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_{G\der})
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}.
\end{align*}
Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$.
\todo{Produce or find a proof.} It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
\end{proof}

@@

[I don't have a proof of this yet.]\todo{Either true or it becomes a condition on $G$.}

\[
\begin{tikzcd}
\CCS(G\der \times G)
& \arrow{l}[shift left,swap]{n^*}
  \arrow{l}[shift right]{p^*}
\CCS(G) 
&&\arrow{ll}[swap]{q^*} 
\CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\
& & \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
\end{tikzcd}
\]
